Value Ordering, Discrepancies, and Restarts for Subgraph Algorithms\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/026842/1 and EP/M508056/1]}

### 2017-12-14 paper/paper.tex
Definite faith

\title{Value Ordering, Discrepancies, and Restarts for Subgraph Algorithms}
\author{Ciaran McCreesh\thanks{This work was supported by the Engineering and Physical Sciences
    Research Council [grant number EP/026842/1]}\\ University of Glasgow, Glasgow, Scotland \\
    ciaran.mccreesh@glasgow.ac.uk}

>>>>

\title{Value Ordering, Discrepancies, and Restarts for Subgraph Algorithms\thanks{This work was
supported by the Engineering and Physical Sciences Research Council [grant numbers EP/026842/1 and EP/M508056/1]}}
\author{Ciaran McCreesh \and Patrick Prosser \and James Trimble\\ University of Glasgow, Glasgow, Scotland \\
    ciaran.mccreesh@glasgow.ac.uk}
